### 2017-11-08 Draft2/Indexing.Growth.tex
Add some polish

@@

% TODO: Explain why you're presenting this algorithm alongside the O(1) algorithm. 1) Simpler 2) 2nd implementation is only fast when g = 2.

>>>>

\HdrLogarithmicImpl

@@

I present this algorithm in addition to the constant time one since 1) it is easier to understand, and 2) the latter is often slower if special circumstances are not met.

\HdrConstantImpl

% TODO: The following needs polish

In this section, I will present the constant time algorithm for indexing a growth array. Before I do so, however, I must establish a mathematical foundation for the algorithm.

I note that every valid index $i$ (``valid'' means $0 \leq i < \VarList.\FieldSize$) can be represented by the ordered pair of integers $(\VarIndexBuffer, \VarIndexElement)$. $\VarIndexBuffer$ is called the \textbf{buffer index} and represents the index of the buffer within the tail. $\VarIndexElement$ is called the \textbf{element index} and represents the index of the element within the buffer.

% TODO: Even more polish

Once these values are determined, the desired item is easily found via [code or math?] $\VarList.\FieldTail[I_B][I_E]$. [I will let $I_B = \VarList.\FieldTail.\FieldSize$ [TODO: Introduce Tsize?] mean that the buffer is $\VarList.\FieldHead$.]

I now derive formulas for $I_B$ and $I_E$ in terms of $i$ [and g and c_0?]. $I_B$ is just the index of the last buffer when $i$ elements are added, or $\VarList.\FieldTail.\FieldSize - 1$
